\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 experience.tex

\subsection{Azure Storage vNext}
\label{sec:cases:azurestore}

%Azure Storage vNext is the next generation storage system for Windows Azure. Azure Storage vNext consists of multiple extent managers, extent nodes, and network engines that are able to send messages across the network, and enqueue any received messages in the input queue of the corresponding node (see Figure~\ref{fig:azurestore}). Each extent manager is responsible for managing a subset of the extent nodes. Each extent node stores its corresponding extent in a local storage, and sends periodical heartbeats and synchronization messages to the extent manager. When the extent manager receives a synchronization message it is responsible to update extent nodes with the latest extent.

%The liveness property that must be always eventually satisfied in the Azure Storage vNext system is that a user-defined $N$ number of extent nodes must be always eventually available with the latest extent. There was an actual bug in the system, that led this property to fail for some very rare executions. Although this buggy behavior would be observed from time to time during stress testing, there was no way to reproduce the bug. We discuss later in this paper, how we are able to detect and reproduce this bug using our approach.

%Azure Storage vNext is very challenging to test. All the unit test and integration test suites of the Azure Storage vNext project successfully pass every single time. However, the developers found that the stress test suite, which constantly kills and launches extent nodes, could fail from time to time after very long executions. The observed failure was that the liveness property described in Section~\ref{sec:overview:bugs} would not get satisfied. The developers had no way to deterministically reproduce this bug or be able to detect what is the culprit, as the traces they were getting were very long and hard to parse.

We used \psharp to test the \emph{distributed extent management} component of the Windows Azure vNext distributed storage system. This component is responsible for managing the partitioned extent metadata and works as follows.

vNext bug goes here.

\subsection{Live Azure Table Migration}
\label{sec:cases:migration}

@@

\subsection{Azure Service Fabric (change to CScale?)}
\label{sec:cases:fabric}

>>>>

\section{Liveness Bug in Azure Storage vNext}
\label{sec:cases:azurestore}

It took only tens of seconds before the testing harness reported the first occurrence of a liveness bug. Upon examining the debug trace, the vNext developers were able to confirm the bug.

However, the trace didn't include enough details, which prevented the developers from identifying a root cause. Fortunately, running the test harness took very little time, so the developers were able to quickly iterate and add more refined debug outputs in each iteration. After several iterations, the developers were able to pinpoint the exact culprit and immediately proposed a solution to fix the bug. Once the proposed solution was implemented, the developers again ran the testing harness, which reported no more bug for $100,000$ iterations in tens of minutes.

The liveness bug occurs in the second testing scenario, where the \texttt{TestingDriver} fails one of the \texttt{ExtentNode} and launches a new one. The \texttt{RepairMonitor} transitions to the hot repairing state and is stuck in the state for infinitely long.

Here is one particular execution sequence resulting in the bug. $i)$ EN$_0$ fails and is detected by the EN expiration loop; $ii)$ EN$_0$ is removed from the EN map; $iii)$ the extent center is updated and the replica count drops from 3, the target, to 2; $iv)$ \texttt{ExtMgr} receives a sync report from EN$_0$; $v)$ the extent center is updated and the replica count increases from 2 to 3 again. This is problematic because, on one hand, the replica count is equal to the target, so the extent repair loop never schedules any repair task. On the other hand, there are only two true replicas in the system, one fewer than the target. This execution sequence leads to one replica missing. Conceivably, repeating this another two times would result in all replicas missing, while \texttt{ExtMgr} still thinks all replicas are healthy. If deployed in production, such bug would have caused a very serious incident of customer data loss.

The culprit is in $iv)$, where \texttt{ExtMgr} receives a sync report from EN$_0$ after deleting the EN. This may occur in \psharp because of arbitrary message interleaving. It may also occur, albeit much less frequently, in the stress testing due to messages being delayed in the network. This explains why the bug only occurs from time to time in the stress testing and also takes long execution to trigger. In contrast, \psharp allows the bug to manifest quickly, the developers to iterate rapidly, the culprit identified promptly, and the fix solution verified effectively, all of which should vastly increase the productivity of distributed storage system development.

\section{Additional Example I: Live Azure Table Migration}
\label{sec:cases:migration}

@@

\section{Additional Example II: Azure Service Fabric (change to CScale?)}
\label{sec:cases:fabric}
